Probing heavy ion collisions using quark and gluon jet substructure

### 2018-02-22 qg_ML.tex
small update to text before pulling
added the new figures to the text, still need to change the captions and text

\begin{figure}[t]
	   \centering
	   \includegraphics[width=0.9\textwidth]{plots/Comp_z.pdf}
	   \caption{Distributions of groomed momentum sharing $z_g$ and TD subjet momentum fraction $z_{\rm T3}$ of quark (left) and gluon (right) jets in pp (solid and dashed lines) and central PbPb (dotted and dot-dashed lines) collisions in \textsc{Jewel}. Note that $z_{\rm cut}<z_g,z_{\rm T3}<0.5$ and $z_{\rm cut}$ is chosen to be 0.1 in this work.}
\label{fig:comp_z}
\end{figure}

@@

\begin{figure}[t]
	   \centering
	   \includegraphics[width=0.9\textwidth]{plots/Comp_rg.pdf}
	   \caption{Distributions of groomed jet radius $r_g$ and TD angular separation between subjets $\theta_{\rm T3}$ of quark (left) and gluon (right) jets in pp (solid and dashed lines) and central PbPb (dotted and dot-dashed lines) collisions in \textsc{Jewel}. The quenched $r_{g}$ distribution is significantly modified.}
\label{fig:comp_rg}
\end{figure}

@@

\begin{figure}[t]
	   \centering
	   \includegraphics[width=0.9\textwidth]{plots/Comp_subjet_m.pdf}
	   \caption{Distributions of TD $\lambda$, which is the ratio between subjet mass and subjet $p_T$, for quark (left) and gluon (right) jets in pp (solid and dashed lines) and centra PbPb (dotted and dot-dashed lines) collisions in \textsc{Jewel}. }
\label{fig:comp_subjet_m}
\end{figure}

@@

\section*{Acknowledgments}
The authors are grateful to Patrick Komiske and Eric Metodiev for collaborating on the development of telescoping deconstruction and contributions to the Appendix. The authors also thank Fr\'ed\'eric Dreyer, Benjamin Nachman, Joern Putschke, Konrad Tywoniuk and Sevil Salur for helpful discussions. We thank Gavin Salam and the participants of the CERN TH institute ``{\sl Novel tools and observables for jet physics in heavy ion collisions}" and the 5-th Heavy Ion Jet Workshop for bringing to our attention the Lund Diagram and its usage in studying jet modifications. YTC was supported by the LHC Theory Initiative Postdoctoral Fellowship under the National Science Foundation grant PHY-1419008. RKE acknowledges partial support from the NSF under Grant No.1067907 \& 1352081 and DOE (need to ask Joern).

>>>>

\begin{figure}[t]
	   \centering
	   \includegraphics[width=0.9\textwidth]{plots/Comp_zg_ppcomp_SD_TD2_new.pdf}
	   \includegraphics[width=0.9\textwidth]{plots/Comp_rg_ppcomp_SD_TD2_new.pdf}
	   \caption{Top: Distributions of groomed momentum sharing $z_g$ (left) and TD subjet momentum  $z_{\rm T2}$ (right); Bottom: Distributions of groomed jet radius $r_g$ and the TD angular separation between subjets $\theta_{\rm T2}$ for of quark (blue) and gluon (red) jets in pp \jw simulations.}
\label{fig:comp_z}
\end{figure}

\begin{figure}[t]
	   \centering
	   \caption{Distributions of groomed jet radius $r_g$ and TD subjet momentum  $z_{\rm T2}$ of quark (blue) and gluon (red) jets in pp.}
\label{fig:comp_z}
\end{figure}

\begin{figure}[t]
	   \centering
	   \includegraphics[width=0.9\textwidth]{plots/Comp_z_new.pdf}
	   \caption{Distributions of groomed momentum sharing $z_g$ and TD subjet momentum fraction $z_{\rm T3}$ of quark (left) and gluon (right) jets in pp (solid and dashed lines) and central PbPb (dotted and dot-dashed lines) collisions in \textsc{Jewel}. Note that $z_{\rm cut}<z_g,z_{\rm T3}<0.5$ and $z_{\rm cut}$ is chosen to be 0.1 in this work.}
\label{fig:comp_z}
\end{figure}

@@

\begin{figure}[t]
	   \centering
	   \includegraphics[width=0.9\textwidth]{plots/Comp_rg_new.pdf}
	   \caption{Distributions of groomed jet radius $r_g$ and TD angular separation between subjets $\theta_{\rm T3}$ of quark (left) and gluon (right) jets in pp (solid and dashed lines) and central PbPb (dotted and dot-dashed lines) collisions in \textsc{Jewel}. The quenched $r_{g}$ distribution is significantly modified.}
\label{fig:comp_rg}
\end{figure}

@@

\begin{figure}[t]
	   \centering
	   \includegraphics[width=0.9\textwidth]{plots/Comp_lambda_new.pdf}
	   \caption{Distributions of TD $\lambda$, which is the ratio between subjet mass and subjet $p_T$, for quark (left) and gluon (right) jets in pp (solid and dashed lines) and centra PbPb (dotted and dot-dashed lines) collisions in \textsc{Jewel}. }
\label{fig:comp_subjet_m}
\end{figure}

@@

\section*{Acknowledgments}
The authors are grateful to Patrick Komiske and Eric Metodiev for collaborating on the development of telescoping deconstruction and contributions to the Appendix. The authors also thank Fr\'ed\'eric Dreyer, Benjamin Nachman, Joern Putschke, Konrad Tywoniuk and Sevil Salur for helpful discussions. We thank Gavin Salam and the participants of the CERN TH institute ``{\sl Novel tools and observables for jet physics in heavy ion collisions}" and the 5-th Heavy Ion Jet Workshop for bringing to our attention the Lund Diagram and its usage in studying jet modifications. RKE also thanks for organizers of the DS@HEP 2017 workshop at FermiLab for an excellent introduction on machine learning techniques. YTC was supported by the LHC Theory Initiative Postdoctoral Fellowship under the National Science Foundation grant PHY-1419008. RKE acknowledges partial support from the NSF under Grant No.1067907 \& 1352081 and DOE (need to ask Joern).
